### 2022-08-09 article.tex
Progress

A more interesting metric is the cyclomatic complexity of the code.
The cyclomatic complexity is defined as the number of ways that
the code can be executed. 
For example, code that has only one \verb|if| statement
has a cyclomatic complexity of 2, as the condition within the \verb|if|
statement can be true or false.
The cyclomatic complexity correlates with code complexity,
where more complex code is likelier to contain bugs.

A feature that deserves more attention
is that 'code must act as a teacher for future developers' \cite{sadowski2018modern}.
Error handling is one of the mechanisms to do so.
For example, let is when calculating the variance of a distribution.
To calculate the variance of a distribution, at least two values
are required. When the variance of only one value is requested,
an error message can helpfully indicate that one needs at least two values.

@@

Publishing raw code is already better than not publishing code at all,
as that raw code can be assumed to have run successfully at least once.
To reproduce an experiment from raw code can be painful, 
yet it is usually better than rewriting the same code from scratch.

@@

There are multiple websites for hosting code, with BitBucket, GitHub,
GitLab and SourceForge being the most well-known.
Of these, GitHub is the most popular website to host code in general,
with millions of users.
GitHub users can create dedicated websites (called 'repositories')
to upload code. Code hosts, such as GitHub, 
store that uploaded code and provide ways 
for visiters to download the code and/or interact with it.
The use of such code hosting websites
accommodates collaboration (\cite{perez2016ten}).
and improves transparency (\cite{gorgolewski2016practical}).
An example from the author is the website \cite{bbbqarticleissue157},
that hosts part of the code for the paper \cite{bilderbeek2022transmembrane},
as shown in Figure \ref{fig:bbbqarticleissue157}.

@@

A more sophisticated check for the code's correctness is
to run units tests and determine the percentage of code that has been
tested, which is called the code coverage. Code coverage
correlates with code quality (\cite{horgan1994,del1995correlation}). 
The non-profit organisation rOpenSci, which peer-reviews code,
has made it a prerequisite to have a code coverage of 100\%.
Also here, CI opens up the possibility to informally annotate the
code coverage. For example, Figure \ref{fig:badge_codecov} shows a 
build badge that indicates that certain R package's code 
has a 100\% code coverage.

@@

Most code hosts, among others, GitHub and GitLab,
automatically keep track of certain metrics.
One such metric is the amount of code each contributor has made.
In that way, authors involved in the writing of the software
are honestly acknowledged. Figure \ref{fig:daisie_contributors}
shows the number of commits the authors of DAISIE (\cite{etienne2020daisie})
have made to its code.

@@

A feature that gets too few attention is that code hosts
allow users to post bug reports and/or ask questions.
This allows other researchers to assess the health
of the code.

@@

Albeith hosted code is vastly superior over raw code
in case of reproduciblity and correctness,
there are some problems with hosted code as well.
The most important one is that hosted code needs maintanance:
the libraries that are used by an experiment
will change over time, inevitably causing the experiment to fail
over time. This process is called bit rot and is a fundamental
problem \richel{ref}. A solution that has more 
longevity is to publishing the code installed in a virtual environment,
as described below.

>>>>

A more interesting metric is the cyclomatic complexity of the code.
The cyclomatic complexity is defined as the number of ways that
the code can be executed. 
For example, code that has only one \verb|if| statement
has a cyclomatic complexity of 2, as the condition within the \verb|if|
statement can be true or false.
The cyclomatic complexity correlates with code complexity,
where more complex code is likelier to contain or give rise to bugs 
(\cite{abd2018calculating,chen2019empirical,zimmermann2008predicting})

A feature that deserves more attention
is that 'code must act as a teacher for future developers' (\cite{sadowski2018modern}).
Error handling is one of the mechanisms to do so.
A simple example is when one (e.g. a BSc student) 
needs to calculate the variance of a distribution.
Commonly one needs to call a function to do so, 
e.g. \verb|var| in R, that needs the values of the distribution
as input.
However, to calculate the variance of a distribution, at least two values
are required. 
When the variance of (zero or) only one value is requested,
an error message can helpfully indicate that the function 
needs at least two values.

@@

Publishing raw code is already better than not publishing code at all,
as that raw code can be assumed to have run successfully at least once.
To reproduce an experiment from raw code can be painful, 
yet it is usually better than writing the same code from scratch.

@@

There are multiple websites for hosting code, with BitBucket, GitHub,
GitLab and SourceForge being the most well-known.
GitHub is currenly the most popular website to host code in general,
with millions of users.
GitHub users can create dedicated websites (called 'repositories')
to upload code. Code hosts, such as GitHub, 
store that uploaded code and provide ways 
for visiters to download the code and/or interact with it.
The use of such code hosting websites
accommodates collaboration (\cite{perez2016ten}).
and improves transparency (\cite{gorgolewski2016practical}).
An example from the author is the website \cite{bbbqarticleissue157},
that hosts part of the code for the paper \cite{bilderbeek2022transmembrane},
as shown in Figure \ref{fig:bbbqarticleissue157}.

@@

Testing, in general, is an important mechanism to ensure
the correctness of code (an interesting example is \cite{rahman2020exploratory}
showing bugs in scientific software on the COVID-19 pandemic. 
It recommends more testing).
The percentage of (lines of) code tested is called the code coverage.
Code coverage correlates with code quality (\cite{horgan1994,del1995correlation}). 
The non-profit organisation rOpenSci (\cite{ram2018community}),
which peer-reviews code,
has made it a prerequisite to have a code coverage of 100\%.
Also here, CI opens up the possibility to informally annotate the
code coverage. For example, Figure \ref{fig:badge_codecov} shows a 
build badge that indicates that certain R package's code 
has a 100\% code coverage.
Hence, code coverage is important metadata, that can automatically
be acquired when using code hosting website.

@@

Most code hosts, among others, GitHub and GitLab,
automatically keep track of certain metrics.
One such metric is the amount of code each contributor has made.
In that way, authors involved in the writing of the software
are honestly acknowledged. Figure \ref{fig:daisie_contributors}
shows the number of commits the authors of DAISIE (\cite{etienne2020daisie})
have made to its code.
The distribution of contributed code per author 
is useful metadata, that can automatically
be acquired when using code hosting website.

@@

A feature that gets too few attention is that code hosts
allow users to post bug reports and/or ask questions.
This allows other researchers to assess the health
of the code.
A healthy project has few open bug reports
and these bug reports should be closed within reasonable time.
When bug reports start to accumulate, this
signals either that the code contained many bugs or that
the developers lost interest in maintaining that code.
The amount of bug reports is useful metadata, 
especially when deciding to use (and depend) on a piece of software.

@@

Albeit hosted code is vastly superior over raw code
in case of reproduciblity and correctness,
there are some problems with hosted code as well.
The most important one is that hosted code needs maintanance:
the libraries that are used by an experiment
will change over time, inevitably causing the experiment to fail
over time. This process is called bit rot and is a fundamental

HIERO

problem \richel{ref}. A solution that has more 
longevity is to publishing the code installed in a virtual environment,
as described below.
